Exploring probability distributions for bivariate temporal granularities

### 2019-08-24 main.Rmd
loading data  for two households

@@

<!-- Refine your search of possible temporal granularities by altering arguments in search_gran() -->

@@

```{r}
data_sm1 %>% granplot("day_week", "hour_day", "general_supply_kwh", plot_type = "decile")

data_sm2 %>% granplot("day_week", "hour_day", "general_supply_kwh", plot_type = "decile")

data_sm3 %>% granplot("day_week", "hour_day", "general_supply_kwh", plot_type = "decile")

>>>>

Let us compare the energy consumption for two households from the customer trials.

@@

For the purpose of this analysis. We only take the data for the year 2013. Let us look at the distribution of energy across coarser temporal granularities and then deep dive into finer temporal granularities.
<!-- Refine your search of possible temporal granularities by altering arguments in search_gran() -->

@@

```{r cust1_hour-day_day-week}
data_sm1 %>% granplot("day_week", "hour_day", "general_supply_kwh", plot_type = "quantile") +  ggtitle("Boxplot of energy consumption for Customer 1")
```
<!-- # ``````{r cust2_hour-day_day-week} -->
<!-- # data_sm2 %>% granplot("day_week", "hour_day", "general_supply_kwh", plot_type = "quantile") + ggtitle("Boxplot of energy consumption for Customer 2") -->
<!-- # ``` -->

``````{r cust3_hour-day_day-week}
data_sm3 %>% granplot("day_week", "hour_day", "general_supply_kwh", plot_type = "quantile") + ggtitle("Boxplot of energy consumption for Customer 3")
```

```{r cust1_hhour-day_day-week}
data_sm1 %>% granplot("day_week", "week_month", "general_supply_kwh", plot_type = "decile") +  ggtitle("Boxplot of energy consumption for Customer 1")
```

<!-- # ```{r cust2_hhour-day_day-week} -->
<!-- # data_sm2 %>% granplot("day_week", "week_month", "general_supply_kwh", plot_type = "decile") + ggtitle("Boxplot of energy consumption for Customer 2") -->
<!-- # ``` -->

```{r cust3_hhour-day_day-week}
data_sm3 %>% granplot("day_week", "week_month", "general_supply_kwh", plot_type = "decile") + ggtitle("Boxplot of energy consumption for Customer 3")
```
